## Proposal

This repository is a draft of the baseline approach I am using for my own time management for the last 6months of my PhD but could easily extended to similar graduate research, professional projects and consulting situations.

#### Outputs {.tabset.tabpills}

The results of the scripts and functions within this repository are focused around the baseline dataset and different combinations of these core variables. The baseline dataset (name: ` `) and core code has been developed and extended from other open source science projects.

##### Stage One: Baseline dataset

```{r}
library(DiagrammeR)
# vignette()

```

Each individual graduate student will have a collection of data, methods and tools needed to conceptualize, create and produce a thesis however by structuring a timeline around key dates (*milestones*) within the same task lists database. This database is based on a simple collection of key variables. To begin with, the standard milestones and key dates can be generated based of each individuals unique starting date using an extension of Bernd's script:

*Milestones*

```{r}
#milestones datset
#generated from bernds R code
```

*Timeline*

This function generates a timeline from the baseline dataset grouped by chapter impact or status....

```{r}

```

*Task lists*

```{r}

```

##### Stage two (updated Oct 2020)

> August2020: I developed this idea further down the track of an interactive web application using shiny.

```{r echo = FALSE}
# shiny::shinyAppDir(
#   system.file("examples/06_tabsets", package="shiny"),
#   options = list(width = "100%", height = 700)
# )
```

> July2020: I developed this idea further down the track of an interactive web application using shiny.

> June2019: This could be done by hand but I have extended Bernds idea of a timeline etc in R for PhD candidates to include better visualisations and other key points. I see this as being an interactive tool for future candidates if I can find funding to annotate the code properly so someone else with no R knowledge can navigate this.

```{r}
# dat <- read.text
```

##### Future stages {.tabset}

With the support of other users there is potential to develop the proposed structure here to create the following extensions of this work.

###### Stage three

Visualise and publish interactive report for SciTech Students. STATUS: [Example of my Phd currently in development]

###### Stage four

Intergrate Outlook emails and tasks

STATUS: [currently methods draft]

###### Stage five

Intergrate Microsoft planner

STATUS: [currently methods draft]

###### Stage six

Internal publishing on uni intranet.[currently methods draft]

*Possible University of Canberra outputs*

```
- Progress Report
- APR
- Research Review
- Scholarship applications
- Timelines
- Future tasklists/goals
```

##### Side projects

[*coming*] 

SEE the`tidyPipes` MANUAL for general concept and approach. This repository contains example data and scripts needed to visualize and communicate multiple different projects including:

- `ACTSeedlings/`[*coming*]
- `DynamicCVs/`[*coming*]
- `flatttingRMDstlyle/` (a repository for documenting and recording reproducible reports for my flatting arrangements).
- `PhDplanningRMDstyle/` (the documentation and reporting for the final 6months of my PhD).
