## Software

```r
# datRSTUDIO <- rstudioapi::versionInfo()
# saveRDS(datRSTUDIO, file = "./data/rStudioDATAinfo.rds")
# datRSTUDIO <- readRDS("./data/rStudioDATAinfo.rds")
```

###### R version

R is currently running `r #eval = FALSE #datRSTUDIO` and Rstudio ...`r #eval = FALSE #datRSTUDIO`

##### R Packages

One of the strengths of working in R is that all the packages and other software needed to develop the operational R libraries (CRAN packages) all open-source and free. The downside of open source science can be the difficultly to reproduce more experimental packages on servers such as `github`.

For the PhD planning template I have began with a `tidyverse` approach and added the additional R packages (as stable as possible) to the notes below. These additional packages are:

*[code here for all packages used....]*

###### `tidyverse`

The general concept of `tidyverse` is to create a collection of R packages that make the following workflow below straightforward, at least in the sense of R functions instead of writing all the functions by hand.

###### `diagrammR`

```{r}
library(DiagrammeR)
```

###### `dataspice`

```{r child = "data/dataSpice4stepGuide.Rmd", eval = T}
library(dataspice)
```

###### `rmarkdown`

[rmarkdown basics]

###### `bookdown`

[bookdown basics]

This is a minimal example of a book based on R Markdown and **bookdown** (https://github.com/rstudio/bookdown). Please see the page "[Get Started](https://bookdown.org/yihui/bookdown/get-started.html)" at https://bookdown.org/yihui/bookdown/ for how to compile this example into HTML. You may generate a copy of the book in `bookdown::pdf_book` format by calling `bookdown::render_book('index.Rmd', 'bookdown::pdf_book')`. More detailed instructions are available here https://bookdown.org/yihui/bookdown/build-the-book.html.

 📜_bookdown.yml


 📜_output.yml


You can find the preview of this example at https://bookdown.org/yihui/bookdown-demo/.

###### `tidyPipes`

[My package under personal development]: Overall, there isn't any methods beyond getting all of my appointments and timelines into a single format to be able to plan my `phd` work and other projects developed around this work.

See the `tidyPipes` manual for more details on the choice of structure and representation.

```{r eval = FALSE}
# datRSTUDIO <- rstudioapi::versionInfo()
# saveRDS(datRSTUDIO, file = "./data/rStudioDATAinfo.rds")
# datRSTUDIO <- readRDS("./data/rStudioDATAinfo.rds")

datR <- R.Version()

grViz("
digraph nicegraph {

  # graph, node, and edge definitions
  graph [compound = true, nodesep = .5, ranksep = .25,
         color = crimson]

  node [fontname = Helvetica, fontcolor = darkslategray,
        shape = rectangle, fixedsize = true, width = 1,
        color = darkslategray]

  edge [color = grey, arrowhead = none, arrowtail = none]

  # subgraph for R information
  subgraph cluster0 {
    node [fixedsize = true, width = 3]
    '@@1-1' -> '@@1-2' -> '@@1-3' -> '@@1-4'
    '@@1-4' -> '@@1-5' -> '@@1-6' -> '@@1-7'
  }

  # subgraph for RStudio information
  subgraph cluster1 {
    node [fixedsize = true, width = 3]
    '@@2' -> '@@3'
  }

  Information             [width = 1.5]
  Information -> R
  Information -> RStudio
  R -> '@@1-1'            [lhead = cluster0]
  RStudio -> '@@2'        [lhead = cluster1]

}

[1]: paste0(names(R.Version())[1:7], ':\\n ', R.Version()[1:7])
[2]: paste0('RStudio version:\\n ', rstudioapi::versionInfo()[[1]])
[3]: paste0('Current program mode:\\n ', rstudioapi::versionInfo()[[2]])

")
```

etc....
